\cvsection{Experience}
\begin{cventries}

  \cventry
    {Research fellow}
    {University of Michigan}
    {Ann Arbor, MI}
    {Current}
    {
 Developed an open source R package for data classification and feature selection. \href{https://github.com/FADHLyemen/lilikoi_summary}{\textbf{Github}}
 \href{https://academic.oup.com/gigascience/article/7/12/giy136/5237705}{\textbf{Paper}}
    }

  \cventry
    {Research fellow}
    {University of Hawaii}
    {Honolulu, HI}
    {2016-2018}
    {
     Lead Data Scientist and Deep Learning developer for features extraction and classification. Used
    Deep Learning techniques such as TensorFlow, H2O, Jupyter.
    \href{ https://www.ncbi.nlm.nih.gov/pubmed/29110491}{\textbf{Deep learning paper}}
    }

  \cventry
    {Data analyst}
    {Henry Ford Health System}
    {Detroit, MI}
    {2016}
    {
      Developed an algorithm to find the association between fMRI images and genomics data using Canonical Correlation Analysis. 
    }

  \cventry
    {AI Advisor}
    {US Department of State}
    {Yemen}
    {2015}
    {
    Advised and helped developed a database of biomedical devices for calibration and maintenance based on FDA regulation and international standards.
    }

  \cventry
    {Assistant professor}
    {University of Science and Technology}
    {Yemen}
    {2009-2015}
    {
    Designed the curriculum of various
    Data Science/ML courses. Evaluated various IoT platforms. Investigated
    technologies such a TensorFlow and OpenCV to run ML algorithms in IoT
    devices.
    }
\end{cventries}


